Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-05 ms.tex
trying to clean up color correction section to reflect the introduction of additional DIRBE bands and single-MBB fits into the analysis

The thermal dust emission model of $\S$\ref{sec:modeling} predicts the 
flux density per solid angle $M_{\nu}$ in e.g. MJy/sr for any single frequency 
$\nu$. In practice, however, we wish to constrain our model using measurements 
in the broad \verb|i100|/\PLANCK~bandpasses, each with $\Delta\nu/\nu\sim0.3$. 
Both the \PLANCK~data and DIRBE data products quote flux density per solid 
angle in MJy/sr under the `IRAS convention'. More precisely, each value 
reported in the \PLANCK~maps gives the amplitude of a power-law spectrum 
with $\alpha$=$-1$, evaluated at the nominal band center frequency, such that 
this spectrum integrated against the transmission reproduces the 
bolometer-measured power. Because our model spectra do not conform to the 
$\alpha$=$-1$ convention, we have computed color correction factors to account 
for the MBB($T$, $\beta$) spectral shape and the transmission as a function of 
frequency:

@@

Here $\nu_{i,c}$ is the nominal band center frequency of band $\nu_i$,  with 
$\nu_{i,c} \in$ \{100, 143, 217, 353, 545, 857, 2997.92458\} GHz. 
$\mathcal{T}_{\nu_i}(\nu)$ represents the relative transmission as a function 
of frequency for band $\nu_i$. For the HFI maps, $\mathcal{T}_{\nu_i}(\nu)$ is 
given by the \PLANCK~transmission curves provided in the file 
\verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. The color correction factors
of Equation \ref{equ:bpcorr} are applied in the sense that 
$b_{\nu_i}(T ,\beta)\times M_{\nu_{i,c}}$ is a prediction suitable for 
direct comparison to the \PLANCK~data products.

For 3000 GHz, we have adopted the DIRBE transmission curve. Since DIRBE-quoted
fluxes also follow the $\alpha$=$-1$ convention, Equation \ref{equ:bpcorr}
remains applicable.

@@

Note that, as in FDS99, $f_2$=(1$-$$f_1$) by convention. Our color correction 
approach allows us to predict $\tilde{I}_{\nu_i}$ by computing monochromatic 
flux densities at the central frequency $\nu_{i,c}$ and then multiplying by 
factors $b_{\nu_i}(T, \beta)$ which are interpolated off of a set of 
precomputed, one-dimensional lookup tables each listing $b_{\nu_i}(T, \beta)$ 
as a function of $T$. We avoided the need to interpolate in both $\beta$ and 
$T$ by computing only a small set of one dimensional correction factors for the
particular set of $\beta$ values of interest 
($\beta \in$ \{1.67, 2.7, 1.19, 2.61\}, see Table \ref{tab:global}).

% need some sort of clarification about the fact that, in the parts of the 
% analysis where beta floats, this precomputation/interpolation is NOT 
% what we do

This color correction approach makes the MCMC sampling described in 
$\S$\ref{sec:mcmc} much more computationally efficient by circumventing the 
need to perform the integral in the numerator of Equation \ref{equ:bpcorr} 
on-the-fly for each proposed dust temperature. We have chosen to compute the 
color corrections on a per-MBB basis because this approach is very 
versatile; all possible two-component models are linear combinations of MBBs, 
so we can apply all of our color correction machinery even when we allow 
parameters other than temperature (e.g. $f_1$) to vary and thereby change the 
dust spectrum shape.

@@

\section{Global Model Parameters}
\label{sec:global}
%%%%

>>>>

The thermal dust emission model of $\S$\ref{sec:modeling} predicts the 
flux density per solid angle $M_{\nu}$ in e.g. MJy/sr for any single frequency 
$\nu$. In practice, however, we wish to constrain our model using measurements 
in the broad DIRBE/\PLANCK~bandpasses, each with $\Delta\nu/\nu\sim0.3$. 
Both the \PLANCK~and DIRBE data products quote flux density per solid 
angle in MJy/sr under the `IRAS convention'. More precisely, each value 
reported in the \PLANCK~maps gives the amplitude of a power-law spectrum 
with $\alpha$=$-1$, evaluated at the nominal band center frequency, such that 
this spectrum integrated against the transmission reproduces the 
bolometer-measured power. Because our model spectra do not conform to the 
$\alpha$=$-1$ convention, we have computed color correction factors to account 
for the MBB($T$, $\beta$) spectral shape and the transmission as a function of 
frequency:

@@

Here $\nu_{i,c}$ is the nominal band center frequency of band $\nu_i$,  with 
$\nu_{i,c} \in$ \{100, 143, 217, 353, 545, 857, 1249.1352, 2141.3747, 
2997.92458\} GHz. $\mathcal{T}_{\nu_i}(\nu)$ represents the relative 
transmission as a function of frequency for band $\nu_i$. For the HFI maps, 
$\mathcal{T}_{\nu_i}(\nu)$ is given by the \PLANCK~transmission curves provided
in the file \verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. For 3000 GHz and
DIRBE 140$\mu$m, 240$\mu$m, we have adopted the corresponding DIRBE 
transmission curves. Again, since DIRBE-quoted fluxes also follow the 
$\alpha$=$-1$ convention, Equation \ref{equ:bpcorr} remains applicable.

% what is the reference for the dirbe

%The color correction factors
%of Equation \ref{equ:bpcorr} are applied in the sense that 
%$b_{\nu_i}(T ,\beta)\times M_{\nu_{i,c}}$ is a prediction suitable for 
%direct comparison to the \PLANCK~data products.

@@

Note that, as in FDS99, $f_2$=(1$-$$f_1$) by convention. Our color correction 
approach allows us to predict $\tilde{I}_{\nu_i}$ by computing monochromatic 
flux densities at the central frequency $\nu_{i,c}$ and then multiplying by 
factors $b_{\nu_i}(T, \beta)$ which are interpolated off of a set of 
precomputed, one-dimensional lookup tables each listing $b_{\nu_i}(T, \beta)$ 
as a function of $T$. We avoided the need to interpolate in both $\beta$ and 
$T$ by computing only a small set of one dimensional correction factors for the
particular set of $\beta$ values of interest (e.g. $\beta$=1.67, 2.7, 
1.63, 2.82 ..., see Table \ref{tab:global}).

% need some sort of clarification about the fact that, in the parts of the 
% analysis where beta floats, i actually do interpolate color corrections 
% off of a 2d grid in (T, beta)

This color correction approach makes the MCMC sampling described in 
$\S$\ref{sec:mcmc} much more computationally efficient by circumventing the 
need to perform the integral in the numerator of Equation \ref{equ:bpcorr} 
on-the-fly for each proposed dust temperature. We have chosen to compute the 
color corrections on a per-MBB basis because this approach is very 
versatile; all possible two-component (and single-MBB) models are linear 
combinations of MBBs, so we can apply all of our color correction machinery 
even when we allow parameters other than temperature (e.g. $f_1$) to vary and 
thereby modify the dust spectrum shape.

@@

% extremely abrupt transition here...
\section{Global Model Parameters}
\label{sec:global}
%%%%
